---
title: "Woking Greens Network"
output: html_document
---

```{r, echo=FALSE, message=FALSE, warning=FALSE, results=FALSE, fig.show='hide'}
# libraries

library(tidyverse)
library(openair)
library(latticeExtra)
library(splitr)
library(lubridate)
library(gganimate)

# set variables
filedir <- "G:/My Drive/IC/Doutorado/Sandwich/Data/WokingNetwork/"

index_names <- c("date",
                 "aqi",
                 "h_aqi",
                 "pm1",
                 "h_pm1",
                 "pm25",
                 "h_pm25",
                 "pm10",
                 "h_pm10",
                 "temp",
                 "h_temp",
                 "l_temp",
                 "rh",
                 "h-rh",
                 "l-rh",
                 "dew",
                 "h_dew",
                 "l_dew",
                 "wetbulb",
                 "h_wetbulb",
                 "l_wetbulb",
                 "heatindex",
                 "h_heatindex")

# make dataframe
data <- data.frame(matrix(ncol=23, nrow=0))
colnames(data) <- index_names
data <- mutate(data,
               date = as.POSIXct(date),
               site = as.factor(NA))

filepaths <- list.files(filedir,
                        full.names = T)

append_file <- function(data,
                        filepaths,
                        index_names.=index_names){
  if(length(filepaths) == 0) return(data) # stop condition of the recursion
  station_number <- filepaths[1] %>% read_file() %>% str_extract("\\d") # get first number in file
  filepaths[1] %>%
    read_csv(col_names = index_names.,
             col_types = cols(date = col_datetime(format = "%d/%m/%y %H:%M"),
                              .default = col_double()),
             skip = 6) %>%
    mutate(site=as.factor(paste("Station",station_number))) %>%
    bind_rows(data) %>%
    append_file(filepaths[-1]) %>%
    return()
}

data <- data %>% append_file(filepaths)
  
# timevar <- data %>%
#   timeVariation(pol = c("pm1","pm25","pm10"), type = "site")

timevar <- data %>%
  timeVariation(pol = c("aqi"), type = "site")
```

# Summary

The air quality monitors seems to be operating properly. There is a good concordance between each station.
Station #7 shows a worse data coverage. It needs further investigation.
The basic statistics, analysis in time and backwards trajectories are below.

Woking seems to do not have intense pollution sources, besides the vehicular fleet.
The diurnal variation presents higher levels of PM in the night (7 pm to 7 am) and in the weekends.

The episodes of intense pollution are associated with air parcels coming from east, passing through London. The days without polluted episodes have parcels coming from west.

# Data consistency

```{r, echo=FALSE, fig.height=15, fig.width=10, warning = FALSE}
summary(data)

data %>%
  filter(site %in% c("Station 1", "Station 2", "Station 3", "Station 4")) %>%
  summaryPlot(pol = c("aqi"),
              period = "months")
data %>%
  filter(site %in% c("Station 5", "Station 6", "Station 7", "Station 8")) %>%
  summaryPlot(pol = c("aqi"),
              period = "months")
```

# Correlations

```{r, fig.height=10, fig.width=10}
M <- data %>%
  select(date, aqi, site) %>%
  pivot_wider(names_from = site, values_from = aqi) %>%
  na.omit() %>%
  select(-date)
M_p <- M %>%
  corrplot::cor.mtest(conf.level = 0.95)
M %>%
  cor() %>%
  corrplot::corrplot.mixed(upper = 'number',
                           lower = 'shade',
                           p.mat = M_p$p,
                           insig = 'p-value')

ani <- data %>%
  select(date, aqi, site) %>%
  pivot_wider(names_from = site, values_from = aqi) %>%
  mutate(day = as.Date(date)) %>%
  select(day, 'Station 1', 'Station 4') %>%
  na.omit() %>%
  ggplot(aes(x = .$'Station 1', y = .$'Station 4')) +
  geom_abline(slope = 1, intercept = 0, alpha = 0.5, linetype = "dashed") +
  geom_point(alpha = 0.1, size = 3) +
  transition_time(day) +
  ease_aes('cubic-in-out') +
  enter_grow(size = 0) + 
  exit_shrink(size = 0) +
  labs(title = 'Day: {frame_time}', x = "Station 1", y = "Station 4") +
  theme_minimal()

ani %>%
  animate(fps = 10,
          duration = 30)

anim_save(filename = "Station1xStation4.gif", path = "G:/My Drive/IC/Doutorado/Sandwich/Output/WokingNetwork/")



```


# Daily mean

```{r, echo=FALSE}
for(sitenumber in c("Station 1", "Station 2", "Station 3", "Station 4", "Station 5", "Station 6", "Station 7", "Station 8")) {
  data %>%
  filter(site == sitenumber) %>%
  calendarPlot(pol = c("aqi"),
               annotate = "value",
               type = "site",
               main = paste("AQI in ", sitenumber))
}



data %>%
  group_by(date) %>%
  summarise(aqi = mean(aqi, na.rm = T)) %>%
calendarPlot(pol = c("aqi"),
             annotate = "value",
             main = paste("AQI"))

```

# Back trajectories

```{r, echo = FALSE}

trajectory_plot_custom <- function (x, show_hourly = TRUE, color_scheme = "cycle_hues") {
  if (inherits(x, "trajectory_model")) {
    if (!is.null(x$traj_df)) {
      traj_df <- x$traj_df
    }
    else {
      stop("There is no data available for plotting.")
    }
  }
  if (inherits(x, "data.frame")) {
    if (all(c("run", "receptor", "hour_along", "traj_dt", 
      "lat", "lon", "height", "traj_dt_i") %in% colnames(x))) {
      traj_df <- x
    }
    else {
      stop("This tibble does not contain plottable trajectory data.")
    }
  }
  dt_runs <- traj_df$traj_dt_i %>% unique() %>% length()
  if (color_scheme == "cycle_hues") {
    colors <- (scales::hue_pal(c = 90, l = 70))(dt_runs)
  }
  else if (color_scheme == "increasingly_gray") {
    colors <- (scales::grey_pal(0.7, 0.1))(dt_runs)
  }
  # traj_df$lon[which(traj_df$lon > 0)] <- traj_df$lon[which(traj_df$lon > 
  #   0)] - (180 * 2)
  receptors <- traj_df %>% dplyr::pull(receptor) %>% unique()
  dates <- traj_df %>% dplyr::pull(traj_dt_i) %>% unique()
  traj_plot <- leaflet::leaflet() %>%
    # leaflet::addProviderTiles(provider = "OpenStreetMap", 
    # group = "OpenStreetMap") %>%
    leaflet::addProviderTiles(provider = "CartoDB.DarkMatter", 
    group = "CartoDB Dark Matter") %>%
    # leaflet::addProviderTiles(provider = "CartoDB.Positron", 
    # group = "CartoDB Positron") %>%
    # leaflet::addProviderTiles(provider = "Esri.WorldTerrain", 
    # group = "ESRI World Terrain") %>%
    # leaflet::addProviderTiles(provider = "Stamen.Toner", 
    # group = "Stamen Toner") %>%
    leaflet::fitBounds(lng1 = min(traj_df[["lon"]]), 
    lat1 = min(traj_df[["lat"]]), lng2 = max(traj_df[["lon"]]), 
    lat2 = max(traj_df[["lat"]])) %>%
    # leaflet::addLayersControl(baseGroups = c("CartoDB Positron", "CartoDB Dark Matter", "Stamen Toner", "ESRI World Terrain"), 
    leaflet::addLayersControl(overlayGroups = c("trajectory_points", "trajectory_paths"), 
    position = "topright")
  for (i in seq_along(receptors)) {
    receptor_i <- receptors[i]
    for (j in seq_along(dates)) {
      date_i <- dates[j]
      wind_traj_ij <- traj_df %>% dplyr::filter(receptor == 
        receptor_i, traj_dt_i == date_i)
      popup <- paste0("<strong>trajectory</strong> ", 
        wind_traj_ij[["traj_dt_i"]], "<br><strong>at time</strong> ", 
        wind_traj_ij[["traj_dt"]], " (", wind_traj_ij[["hour_along"]], 
        " h)<br><strong>height</strong> ", wind_traj_ij[["height"]], 
        " <font size=\"1\">m AGL</font> / ", "<strong>P</strong> ", 
        wind_traj_ij[["pressure"]], " <font size=\"1\">hPa</font>")
      traj_plot <- traj_plot %>% leaflet::addPolylines(lng = wind_traj_ij[["lon"]], 
        lat = wind_traj_ij[["lat"]], group = "trajectory_paths", 
        weight = 2, smoothFactor = 1, color = colors[j]) %>% 
        leaflet::addCircles(lng = wind_traj_ij[["lon"]], 
          lat = wind_traj_ij[["lat"]], group = "trajectory_points", 
          radius = 250, fill = TRUE, color = colors[j], 
          fillColor = colors[j], popup = popup)
    }
  }
  traj_plot
}

getMet <- function (dates, path_met = "G:/My Drive/IC/Doutorado/Sandwich/Data/TrajData/") {
  
  dates <- dates %>%
    format(format = "%y-%b") %>%
    unique()
  
  for (date in dates) {
    for (week in 1:5) {
      year <- str_split_fixed(date, "-", n = 2)[1]
      month <- str_to_lower(str_split_fixed(date, "-", n = 2)[2])
      try(download.file(url = paste0("ftp://arlftp.arlhq.noaa.gov/archives/gdas1/gdas1.",
                                   month,
                                   year,
                                   ".w",
                                   week),
                      destfile = paste0(path_met,"gdas1.", month, year, ".w", week),
                      mode = "wb")
      )
    }
  }
}

#getMet(dates = data$date) #import gdas1 data from NOAA. Run weekly.

```

```{r, echo = FALSE}

event_days <- data %>%
  mutate(date = floor_date(date, "day")) %>%
  group_by(date) %>%
  summarise(mean_aqi = na.omit(mean(aqi))) %>%
  slice_max(mean_aqi, n = 3) %>%
  pull(date) %>%
  strftime(format="%Y-%m-%d") %>%
  unique() %>%
  sort()

normal_days <- data %>%
  mutate(date = floor_date(date, "day")) %>%
  group_by(date) %>%
  summarise(mean_aqi = na.omit(mean(aqi))) %>%
  slice_min(mean_aqi, n = 3) %>%
  pull(date) %>%
  strftime(format="%Y-%m-%d") %>%
  unique() %>%
  sort()

events_trajectory <- list()
n = 1
for (day in event_days){
  events_trajectory[[n]] <- 
    hysplit_trajectory(
      lat = 51.318282,
      lon = -0.558610,
      height = 50,
      duration = 24,
      days = day,
      daily_hours = c(0, 6, 12, 18),
      direction = "backward",
      met_type = "gdas1",
      extended_met = TRUE,
      met_dir = "G:/My Drive/IC/Doutorado/Sandwich/Data/TrajData/",
      exec_dir = "G:/My Drive/IC/Doutorado/Sandwich/Data/HysplitOutput/") 
  saveRDS(events_trajectory[[n]], paste0("G:/My Drive/IC/Doutorado/Sandwich/Data/TrajProc/", "events_trajectory", n, "0.RData"))
  n <- n + 1
}

normal_trajectory <- list()
n = 1
for (day in normal_days){
  normal_trajectory[[n]] <- 
    hysplit_trajectory(
      lat = 51.318282,
      lon = -0.558610,
      height = 50,
      duration = 24,
      days = day,
      daily_hours = c(0, 6, 12, 18),
      direction = "backward",
      met_type = "gdas1",
      extended_met = TRUE,
      met_dir = "G:/My Drive/IC/Doutorado/Sandwich/Data/TrajData/",
      exec_dir = "G:/My Drive/IC/Doutorado/Sandwich/Data/HysplitOutput/") 
  saveRDS(events_trajectory[[n]], paste0("G:/My Drive/IC/Doutorado/Sandwich/Data/TrajProc/", "normal_trajectory", n, "0.RData"))
  n <- n + 1
}

```

## Days with wrost AQI

```{r, echo = FALSE}
events_trajectory[[1]] %>% trajectory_plot_custom()
events_trajectory[[2]] %>% trajectory_plot_custom()
events_trajectory[[3]] %>% trajectory_plot_custom()
```

## Days with best AQI

```{r, echo = FALSE}
normal_trajectory[[1]] %>% trajectory_plot_custom()
normal_trajectory[[2]] %>% trajectory_plot_custom()
normal_trajectory[[3]] %>% trajectory_plot_custom()
```

# Variations in time

## Diurnal variation

```{r, echo=FALSE}
plot(timevar, subset = "hour")
```

## Diurnal variation by weekday

```{r, echo=FALSE, fig.height=10, fig.width=10}
plot(timevar, subset = "day.hour")
```

## Weekly averages

```{r, echo=FALSE}
plot(timevar, subset = "day")
```

## Monthly averages

```{r, echo=FALSE}
plot(timevar, subset = "month")
```

## stats

```{r}

```

